Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
style edit: denoting limits using lim_{} and only using \xrightarrow when necessary

% proposition b_2 to \infty
\begin{proposition}
	Assuming assumption \ref{assumption}, and if
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	then
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
\label{prop:b2_to_infty}
\end{proposition}
\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
	\end{IEEEeqnarray*}
	Idem, for all $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
	and
	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$

@@

\begin{proof}
	% case when b2 bar \to infty
	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{\bar{b}_2} \to 0, \quad B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
	\qquad
	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
	and, for all $t \in [0,T)$:
	\begin{equation*}
	\begin{array}{l}
	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
	\end{array}
	\end{equation*}

@@

	Hence, for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
	\begin{equation*}
	\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon.
	\end{equation*} 
	Since the proof holds for arbitrary $\epsilon > 0$, we obtain:
	\begin{equation*}
	\lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} = 0.
	\end{equation*}
	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $w^{\bar{b}_2}_0 \geq 0$ and $w^{\bar{b}_2}_0 \xrightarrow[\bar{b}_2 \to \infty]{} 0$. Thus, we obtain:
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty,$$
	and conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$

>>>>

% proposition b_2 to \infty
\begin{proposition}
	Assuming assumption \ref{assumption}, and if
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	then
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
\label{prop:b2_to_infty}
\end{proposition}
\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\lim_{b_2 \to \infty}\delta^{+,b_2}_u - \delta^{-,b_2}_u = +\infty$.
	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
	\end{IEEEeqnarray*}
	Idem, for all $t \in [0,T)$,
	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
	and
	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$

@@

\begin{proof}
	% case when b2 bar \to infty
	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{\bar{b}_2} \to 0, \quad B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
	\qquad
	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
	and, for all $t \in [0,T)$:
	\begin{equation*}
	\begin{array}{l}
	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t = (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2) w_t^{\bar{b}_2} = (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
	\end{array}
	\end{equation*}

@@

	Hence, for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
	\begin{equation*}
	\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon.
	\end{equation*} 
	Since the proof holds for arbitrary $\epsilon > 0$, we obtain:
	\begin{equation*}
	\lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} = 0.
	\end{equation*}
	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $w^{\bar{b}_2}_0 \geq 0$ and $\lim_{\bar{b}_2 \to \infty}w^{\bar{b}_2}_0 = 0$. Thus, we obtain:
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty,$$
	and conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
